The `geomnet` package

### 2016-12-06 README.Rmd
add plotly code example

>>>>

## Interactivity with `plotly`!

Now including interactivity with `ggplotly()`!

```{r football, eval = FALSE}
library(geomnet)
# devtools::install_github("ropensci/plotly")
library(plotly)
data("football")
# data step: merge vertices and edges
ftnet <- fortify(as.edgedf(football$edges), football$vertices)

# create data plot
gg <- ggplot(data = ftnet,
       aes(from_id = from_id, to_id = to_id)) +
  geom_net(layout.alg = 'fruchtermanreingold',
    aes(colour = value, group = value,
        linetype = factor(same.conf != 1)),
    linewidth = 0.5,
    size = 5, vjust = -0.75, alpha = 0.3) +
  theme_net() +
  theme(legend.position = "bottom") +
  scale_colour_brewer("Conference", palette = "Paired")  +
  guides(linetype = FALSE)
ggplotly(gg)
```
